% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Yu Gu}

\basicInfo{
  \addr{Sunnyvale 94085} \textperiodcentered\
  \email{grain1101@gmail.com} \textperiodcentered\
  \phone{(+1) 669-246-8478} \textperiodcentered\
  \linkedin[Yu Gu]{https://www.linkedin.com/in/yu-gu-2978b0102/}}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C++, C\#, Java, Javascript, PowerShell, Linux shell
  \item Environment: Windows, Unix/Linux
  \item Experienced: Web services, Networking, Enterprise Software(Office 365)
\end{itemize}

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Microsoft Corp.} Suzhou, China}{2015.07 -- 2016.11}
\role{Software Engineer}{Manager: Mushi Jin}
Backend software engineer working at Microsoft SharePoint team. Project experiences are Project SharePoint Hybrid Taxonomy and Project ODB Cross-Geo Data Move.
\begin{itemize}
\item Developing languages include C\#, Powershell.
\item Platforms include Cosmos, SQL Server, Azure, etc.
\end{itemize}

\datedsubsection{\textbf{Project SharePoint Hybrid Taxonomy}}{2015.07 -- 2016.04}
\role{C\#, Cosmos, CSOM, SQL, Restful-like, timer jobs}{ }
Hybrid Taxonomy replicates the metadata groups that are mastered in SharePoint Online to on-premises periodically
while keeping the on-premises copies Read Only.
\begin{itemize}
  \item Tree-structured metadata migration.
  \item Designing and developing the main feature, adding unit tests, writing docs.
  \item performance analysis via a Microsoft's internal Bigdata platform Cosmos.
\end{itemize}

\datedsubsection{\textbf{Project SharePoint Online MultiGeo}}{2016.04 -- 2016.11}
\role{C\#, Cmdlets, NoSQL, SharePoint-Online, OneDrive for Business, Azure} { }
MultiGeo project changes the basic infrastructure of SPO and implements data move for ODB and tenant data. This is to meet data residency laws,
to save costs and to enrich productivity experience.
\begin{itemize}
  \item Tenant admin triggers requests to another region via Cmdlets and sends to servers through restful API.
  \item Background workflow includes backing up, uploading to Azure, downloading, restoring and cleanup.
\end{itemize}

\section{\faUsers\ Internship}
\datedsubsection{\textbf{Baidu Inc.} Beijing, China}{2014.12 -- 2015.02}
\role{Frontend Deverloper Intern}{}
Internship in Baidu Image team. Developed a user feedback web application.
\begin{itemize}
\item Developing languages including Javascript, JQuery, HTML/CSS
\end{itemize}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Northeast Normal University(NENU)}, ChangChun, Jilin, China}{2012 -- 2015}
\textit{M.S.} in Computer Science(CS)
\datedsubsection{\textbf{Northeast Normal University(NENU)}, ChangChun, Jilin, China}{2008 -- 2012}
\textit{B.S.} in Computer Science(CS)

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}


\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item GitHub: https://github.com/grain1101
  \item Languages: English - Fluent, Mandarin - Native speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
